%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Russell Abernethy} % Your name
\address{https://github.com/rabernethy \\ www.linkedin.com/in/russell-d-abernethy} 
\address{(215)~$\cdot$~817~$\cdot$~3257 \\ russell.abernethy@temple.edu}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Temple University, College of Science \& Technology} \hfill {\em December 2022}    \\ 
B.S. in Computer Science                                                                \\
Certificate in Computer Security \& Digital Forensics                                   \\
\smallskip                                                                              \\
Overall GPA: 3.76

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Integrative Ecology Lab @ Temple University}{June 2021 - Present}{Undergraduate Research Assistant}{Philadelphia, PA}
\item Developed automation software for data cleaning location data.
\item Helped implement a pipeline for weather data from NWS's open API.
\item Worked on a computer vision research project focused on classifying spotted lanternfly by their phenology from a database provided by the PA Department of Agriculture.
\item Used high performance computing cluster for computer vision research.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Temple University Physics Department}{August 2021 - Present}{Classroom Assistant}{Philadelphia, PA}
\item Provided support to the Professor during lecture by passing back assignments and taking attendance.
\item Aided students during breakout problem sessions by being available for questions and offering hints when stuck.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Ockanickon Scout Reservation}{June 2019 - Augest 2020}{Logistics Coordinator \& Office Manager}{Pipersville, PA}
\item Oversaw \& trained a team of office staff that would greet and answer customer questions.
\item Optimally fit customers into housing based on different criteria, such as medical need, each week.
\item Handled customer relations before their arrival on property.
\item Managed emergency preparedness drill each week and was point person in event of a real emergency.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Other Skills \& Experiences}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages  & C, C++, Python3, Java, \& JavaScript                                      \\
Relevant Course Work& Data Structures \& Algorithms, Independent Research, \& Software Design   \\
Tools               & Visual Studio Code, Git, NodeJS, \& React                                    \\
Other Achievements  & Eagle Scout
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
